Insecticide resistance evolution with mixtures and sequences : a model-based explanation.

### 2017-09-11 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
paper writing

---
title: "Insecticide resistance evolution with mixtures and sequences : a model-based explanation."
output: 
  pdf_document:
    #citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex

#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
bibliography: library.bib
csl: biomed-central.csl
fontsize: 11pt
spacing: double
# below worked in test_linenumbers.Rmd
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
---

```{r, eval=FALSE, include=FALSE}
#!!!! paper protocol
#!!!! might be easier to put text and figs into separate Rmd files after draft stage
#!!!! drafts knit to pdf with pdf_document in YAML and this chunk eval=FALSE
#!!!! submission MS, knit to word_document, YAML, this chunk eval=FALSE, 
#!!!!  in WORD: delete figs, add fig numbers to fig legends, set double space, add line numbers 
#!!!! submission figs, set this chunk to eval=TRUE

>>>>

---
title: "Insecticide resistance evolution with mixtures and sequences : a model-based explanation."
# output: 
#   pdf_document:
#     keep_tex: true
#     fig_caption: true
#     latex_engine: pdflatex

output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
bibliography: library.bib
csl: biomed-central.csl
fontsize: 11pt
spacing: double
# below worked in test_linenumbers.Rmd
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
---

```{r, eval=FALSE, include=FALSE}
#!!!! paper protocol
#!!!! submission MS, knit to word_document, YAML, this chunk eval=FALSE, 
#!!!!  in WORD: delete figs, add fig numbers to fig legends, set double space, add line numbers 
#!!!! submission figs, set this chunk to eval=TRUE
#!!!! previous drafts knitted to pdf with pdf_document in YAML and this chunk eval=FALSE
